---
title: "knapsack-vignette"
author: "SILA KILICOGLU (silki753@student.liu.se) and SAMI FURKAN YILDIRIM (samyi572@student.liu.se)"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{knapsack-vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## **Description**
The package contains three different functions (brute_force_knapsack, greedy_knapsack, knapsack_dynamic), which are used brute force search, dynamic and greedy algorithms, for solving what is called the knapsack problem.

## **Import**

```{r setup}
library(parallel)
library(knapsack)
```

## **Arguments**
All three functions use the same argument:
_x_
: A data frame with two variables v (value) and w (weigth)
_W_
: The variable is the knapsack size.

## **Functions**
_**Brute Force Search**_:
For this function, there is an option argument called parallel and default value is FALSE.
```r
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500)
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000)
```
If parallel argument set to TRUE, then the function parallelizes over the detected cores.

```r
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500, parallel = TRUE)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 3500, parallel = TRUE)
brute_force_knapsack(x = knapsack_objects[1:8,], W = 2000, parallel = TRUE)
brute_force_knapsack(x = knapsack_objects[1:12,], W = 2000, parallel = TRUE)

```

Without parallelizing brute force search, it takes:

```r
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000))
```
For profile code:
```r
library(profvis)
profvis(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000))
```


With parallelizing brute force search, it takes:

```r
system.time(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000, parallel = TRUE))
```
_Question: What performance gain could you get by parallelizing brute force search?_ \newline
_It speeds up the execution of the code._

For profile code:
```r
library(profvis)
profvis(brute_force_knapsack(x = knapsack_objects[1:16,], W = 2000, parallel=TRUE))
```

_**Dynamic Programming**_:
For $n = 500$ objects, it takes: 
```r
system.time(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```
For profile code:
```r
library(profvis)
profvis(knapsack_dynamic(x = knapsack_objects[1:500,], W = 3500))
```

_**Greedy Heuristic**_:

```r
greedy_knapsack(x = knapsack_objects[1:800,], W = 3500)
greedy_knapsack(x = knapsack_objects[1:1200,], W = 2000)
```

For $n = 1000000$ objects, it takes:  
```r
system.time(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```

For profile code:
```r
library(profvis)
profvis(greedy_knapsack(x = knapsack_objects[1:1000000,], W = 3500))
```


## *Important Note*

These three functions don't give always the same results:

```r
greedy_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

```r
brute_force_knapsack(x = knapsack_objects[1:8,], W = 3500)
```

```r
knapsack_dynamic(x = knapsack_objects[1:8,], W = 3500)
```